figures and calculations for global fisheries management

### 2019-01-11 documents/figs-and-calcs.Rmd
a few improvements to catch share regression

downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
                              y = factor(join_mutate$CatchShare),
                              yname = "CatchShare")

itq_broad_fit <-
  glm(
    formula = CatchShare ~ gdp_center + MainCat,
    family = "binomial",
    data = downjoin
  )

@@

aug_itq_broad_fit %>% 
  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
  geom_boxplot()

@@

plot(bayes_itq_broad_fit)

pps = rstanarm::posterior_predict(bayes_itq_broad_fit) %>% 
  colMeans()

aug_itq_broad_fit <- broom::augment(bayes_itq_broad_fit) %>% 
  mutate(pred = pps)

aug_itq_broad_fit %>% 
  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
  geom_boxplot()

>>>>

downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
                              y = factor(join_mutate$CatchShare),
                              yname = "CatchShare")
downjoin %>% 
  ggplot(aes(log(MSY),fill = CatchShare)) + 
  geom_density()

itq_broad_fit <-
  glm(
    formula = CatchShare ~ gdp_center + MainCat + log(MSY),
    family = "binomial",
    data = downjoin
  )

@@

orig_itq_broad_fit <- join_mutate %>% 
  mutate(pred = predict(itq_broad_fit, type = "response", newdata = join_mutate))

catchshare_pred_plot <- orig_itq_broad_fit %>% 
  ggplot(aes(pred,CatchShare == 1,fill = CatchShare == 1)) + 
  ggridges::geom_density_ridges(show.legend = FALSE) +
  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
  labs(y = "Is Catch Share?",
       x = "Probability of Catch Share",
       caption = "Classified as catch share if p>0.5")

@@

catchshare_pred_plot

g <- pROC::roc(CatchShare ~ pred, data = orig_itq_broad_fit)

pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red")
